### 2016-08-18 p01-ch01-2012/paper.tex
Apply formatting and typography fixes
- Fix the mis-referenced listings and figures
- Fix typos

Signed-off-by: Behrooz Nobakht <nobeh5@gmail.com>

\chapter[Application-Level Scheduling]{Programming and Deployment of Active Objects with Application-Level Scheduling%
\footnote{This work is partially supported by the EU FP7-231620 project: HATS.}}
% 
\label{ch:p01:ch01}
% 
\chapterauthor{Behrooz Nobakht, Frank S. de Boer, Mohammad Mahdi Jaghoori,  Rudolph Schlatte}

@@

\begin{lstlisting}[float=t, label=lst:exres, caption=Exclusive Resource in Creol %, multicols=2
]
interface Resource begin
	(* \label{ch01:lst:priority_range} *)(*
	%with User  \label{ch01:lst:with} 
	*)
		op request()
		op release()
end

>>>>

\chapter[Application-Level Scheduling]{Programming and Deployment of Active Objects with Application-Level Scheduling%
\footnote{This work is partially supported by the EU FP7-231620 project: HATS.}}
% 
\label{ch:p01:ch01}
% 
\chapterauthor{Behrooz Nobakht, Frank S. de Boer, Mohammad Mahdi Jaghoori, Rudolf Schlatte}

@@

\begin{lstlisting}[float=t, label=ch01:lst:exres, caption=Exclusive Resource in Creol]
interface Resource begin
	(* \label{ch01:lst:priority_range} *)(*
	%with User  \label{ch01:lst:with} 
	*)
		op request()
		op release()
end

### 2016-08-18 p01-ch02-2013/paper.tex
Apply formatting and typography fixes
- Fix the mis-referenced listings and figures
- Fix typos

Signed-off-by: Behrooz Nobakht <nobeh5@gmail.com>

\lstset{language=Creol,escapeinside={(*}{*)}} 
% \vspace{-20pt}
\begin{lstlisting}[float=h, label=lst:try:catch, caption=Using try-catch for processing future values]
try {
	x = f.get(e)
	S_1
} catch(Exception x) {
	S_2
}
\end{lstlisting}
% \vspace{-20pt}

@@

\lstset{language=Creol,escapeinside={(*}{*)}} 
\begin{center}
\begin{minipage}[t]{0.48\textwidth}
% \vspace{-25pt}
\begin{lstlisting}[label=lst:frh:polling, caption=With polling]
class DataProcessor begin
	op process(d: Data) ==
		var p := allocDataProcessor(d)
		p ! process (d)
		do {
			s := p ! getStatus (d)
			if (s <> nil)
				var r := p ! getResults(d)
				publishResult(r)
			wait(TimeUnit.toSecond(1))
		} while (true)
end
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
% \vspace{-25pt}
\begin{lstlisting}[label=lst:frh:deadlines, caption=With deadlines]
class DataProcessor begin
	op process(d: Data) == 
		var p := allocDataProcessor(d)
		var D := estimateDeadline(d)
		var f := 
			p ! process (d) deadline (D)
		try {
			publishResult(f.get())
		} catch (Exception x) {
			if (f.isAborted)
				notifyFailure(d)
		}
end 
\end{lstlisting}
\end{minipage}
% \vspace{-10pt}
\end{center}

@@

\lstset{language=Creol,escapeinside={(*}{*)}} 
\begin{center}
\begin{minipage}[t]{0.48\textwidth}
% \vspace{-30pt}
\begin{lstlisting}[label=lst:frh:dm, caption=Data Processor class]
class DataProcessor begin
	var scheduler := new DataScheduler()
	op process(d: Data) ==
		// do process
end
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
% \vspace{-30pt}
\begin{lstlisting}[label=lst:frh:sched, caption=Custom scheduler]
class DataScheduler extends DefaultSchedulingManager {
	boolean isPrior(Process p1, Process p2) {
		if (p1.getCustomer().equals("A")) {
			return true;
		}
		return super.isPrior(p1, p2);
	}
}
\end{lstlisting}
\end{minipage}
% \vspace{-15pt}
\end{center}

@@

\begin{table}[h]
% \begin{wraptable}{l}{0.25\textwidth}
% \vspace{-15pt}
\begin{tabular}{c c}\thickhline
$s_1$ & $s_2$ \\ \thickhline
$88.71\%$ & $94.57\%$ \\ \hline
\end{tabular}
\caption{Evaluation Results}
\label{ch02:tbl:eval}
% \vspace{-15pt}
% \end{wraptable}
\end{table}

>>>>

\lstset{language=Creol,escapeinside={(*}{*)}} 
% \vspace{-20pt}
\begin{lstlisting}[float=h, label=ch02:lst:try:catch, caption=Using try-catch for processing future values]
try {
	x = f.get(e)
	S_1
} catch(Exception x) {
	S_2
}
\end{lstlisting}
% \vspace{-20pt}

@@

\lstset{language=Creol,escapeinside={(*}{*)}} 
\begin{center}
\begin{minipage}[t]{0.48\textwidth}
% \vspace{-25pt}
\begin{lstlisting}[label=ch02:lst:frh:polling, caption=With polling]
class DataProcessor begin
	op process(d: Data) ==
		var p := allocDataProcessor(d)
		p ! process (d)
		do {
			s := p ! getStatus (d)
			if (s <> nil)
				var r := p ! getResults(d)
				publishResult(r)
			wait(TimeUnit.toSecond(1))
		} while (true)
end
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
% \vspace{-25pt}
\begin{lstlisting}[label=ch02:lst:frh:deadlines, caption=With deadlines]
class DataProcessor begin
	op process(d: Data) == 
		var p := allocDataProcessor(d)
		var D := estimateDeadline(d)
		var f := 
			p ! process (d) deadline (D)
		try {
			publishResult(f.get())
		} catch (Exception x) {
			if (f.isAborted)
				notifyFailure(d)
		}
end 
\end{lstlisting}
\end{minipage}
% \vspace{-10pt}
\end{center}

@@

\lstset{language=Creol,escapeinside={(*}{*)}} 
\begin{center}
\begin{minipage}[t]{0.48\textwidth}
% \vspace{-30pt}
\begin{lstlisting}[label=ch02:lst:frh:dm, caption=Data Processor class]
class DataProcessor begin
	var scheduler := new DataScheduler()
	op process(d: Data) ==
		// do process
end
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
% \vspace{-30pt}
\begin{lstlisting}[label=ch02:lst:frh:sched, caption=Custom scheduler]
class DataScheduler extends DefaultSchedulingManager {
	boolean isPrior(Process p1, Process p2) {
		if (p1.getCustomer().equals("A")) {
			return true;
		}
		return super.isPrior(p1, p2);
	}
}
\end{lstlisting}
\end{minipage}
% \vspace{-15pt}
\end{center}

@@

\begin{table}[t]
\centering
% \begin{wraptable}{l}{0.25\textwidth}
% \vspace{-15pt}
\begin{tabular}{c c}
\toprule
$s_1$ & $s_2$ \\ 
\toprule
$88.71\%$ & $94.57\%$ \\ 
\bottomrule
\end{tabular}
\caption{Evaluation Results}
\label{ch02:tbl:eval}
% \vspace{-15pt}
% \end{wraptable}
\end{table}

### 2016-08-18 p02-ch01-2014/paper.tex
Apply formatting and typography fixes
- Fix the mis-referenced listings and figures
- Fix typos

Signed-off-by: Behrooz Nobakht <nobeh5@gmail.com>

\lstset{language=Java}
\begin{center}
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[caption=Ping as an interface,label=lst:ping:interface]
public interface IPing {
  void ping(String msg);
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[caption=Pong as an interface,label=lst:pong:interface]
public interface IPong {
  void pong(String msg);
}
\end{lstlisting}
\end{minipage}
\end{center}

@@

\lstset{language=Java}
\begin{center}
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[caption=Ping actor in Akka,label=lst:ping:akka]
public class Ping(ActorRef pong)
  extends UntypedActor 
  implements IPing {

@@

  public void onReceive(Object m) {
    if (!(m instanceof String)) {
      // Message not understood.
    } else 
    if (((String) m).startsWith("pinged") {
      // Explicit cast needed.
      ping((String) m);
    } 
   }
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[caption=Pong class in Akka,label=lst:pong:akka]
public class Pong 
  extends UntypedActor 
  implements IPong {

@@

\begin{figure}[h]
% \begin{wrapfigure}{r}{0.48\textwidth}
% \vspace{-20pt}
\begin{lstlisting}[caption=main in Akka,label=lst:main:akka]
ActorSystem s = ActorSystem.create();
ActorRef pong = s.actorOf(Props.create(Pong.class));
ActorRef ping = s.actorOf(Props.create(Ping.class, pong));
ping.tell(""); // To get a Future
\end{lstlisting}
% \vspace{-20pt}
% \end{wrapfigure}
\end{figure}

@@

\lstset{language=Java}
\begin{figure}[h]
% \begin{wrapfigure}{r}{0.48\textwidth}
% \vspace{-20pt}
\begin{lstlisting}[caption=main in ABS,label=lst:main:ABS]
ABSIPong pong;
pong = new ABSPong;
ping = new ABSPing(pong);
ping ! ping("");
\end{lstlisting}
% \vspace{-20pt}
% \end{wrapfigure}
\end{figure}

@@

\lstset{language=abs}
\begin{center}
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[caption=Ping in ABS,label=lst:ping:abs]
interface ABSIPing {
  Unit ping(String msg);
}
class ABSPing(ABSIPong pong) implements ABSIPing {
  Unit ping(String msg) {
  pong ! pong("ponged," + msg);
  }
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[caption=Pong in ABS,label=lst:pong:abs]
interface ABSIPong {
  Unit pong(String msg);
}
class ABSPong implements ABSIPong {
  Unit pong(String msg) {
    sender ! ping( "pinged," + msg);
  }
}
\end{lstlisting}
\end{minipage}
\end{center}
\lstset{language=Java}

@@

\begin{center}
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[caption=Actor interface (1) ,label=lst:j8:run]
public interface Actor {
  public void run() {
    Object m = queue.take();

@@

  // continue to the right
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[caption=Actor interface (2),label=lst:j8:enq]

@@

\paragraph{Modeling Asynchronous Messages} 
\label{ch03:par:asynchronous_messages}
We model an asynchronous call 
$$
\jtt{Future<V>} \; f = e_0\; !\; m(e_1,\ldots,e_n)
$$
to a method in ABS by the Java~8 code snippet of Listing \ref{ch03:lst:j8:call0}.
The final local variables $\jtt{u}_1$, $\ldots$, $\jtt{u}_n$ (of the caller) are used to store the values of
the Java~8 expressions $\jtt{e}_1$, $\ldots$, $\jtt{e}_n$ corresponding to the actual parameters  $e_1,\ldots,e_n$.
The types \jtt{T}$_i$, $i=1,\ldots,n$,  are the corresponding Java~8 types of  $e_i$, $i=1,\ldots,n$.
\begin{center}
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[mathescape,caption=Async messages with futures,label=lst:j8:call0]
final T$_1$ u$_1$ = e$_1$;
. . . 
final T$_n$ u$_n$ = e$_n$;
Future<V> v = e$_0$.send(
  () $\to$ { return m(u$_1$,$\ldots$,u$_n$); }
);
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[mathescape,caption=Async messages w/o futures,label=lst:j8:call1]
final T$_1$ u$_1$ = e$_1$;
. . . 
final T$_n$ u$_n$ = e$_n$;
e$_0$.send(
  { () $\to$ m(u$_1$,$\ldots$,u$_n$); }
);
\end{lstlisting}
\end{minipage}
\end{center}

@@

\begin{center}
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[mathescape, caption=Ping as an Actor,label=lst:ping]
public class Ping(IPong pong) implements IPing, Actor {
 public void ping(String msg) {
  pong.send( () $\to$ { pong.("ponged," + msg) } );
  }
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[mathescape, caption=Pong as an Actor,label=lst:pong]
public class Pong implements IPong, Actor {
  public void pong(String msg) {
    sender().send(( ) $\to$ { ping.("pinged," + msg) } );
  }
}
\end{lstlisting}
\end{minipage}
\end{center}

@@

\paragraph{Modeling Cooperative Scheduling}
The ABS statement $\bfjtt{await}\; g$, where $g$ is a boolean guard, allows an active object to preempt the current method and schedule another one.
% We describe the  translation of await statements in the context of a general translation of statements in the ABS language.
We model cooperative scheduling by means of a call to the \jtt{await} method in Listing~\ref{ch03:lst:j8:await}.
Note that the preempted process is thus passed as an additional parameter and as such queued in case the guard is false,
otherwise it is executed.
Moreover, the generation of the continuation of the process is an optimization task for the code generation process to prevent code duplication.
\begin{center}
\begin{minipage}[t]{0.48\textwidth}
% \begin{lstlisting}[mathescape, caption=Java~8 conceptual await,label=lst:j8:await]
%  this.await($b$, $()\rightarrow \{S\}$)
%  // S is the continuation
% \end{lstlisting}
\begin{lstlisting}[mathescape,caption=main in ABS API,label=lst:main:api]
IPong pong = new Pong();
IPing ping = new Ping(pong);
ping.send(
  () -> ping.ping("")
);
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[mathescape,caption=Java~8 await implementation,label=lst:j8:await]
void await(final Boolean guard, 
           final Runnable cont) {
  if (!guard) { 
    this.send(() $\to$ 
      { this.await(guard, cont) })
  } else { cont.run() }
}
\end{lstlisting}
\end{minipage}
\end{center}

@@

\begin{center}
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[caption=Remote ping actor main,label=lst:ping:remote]
Properties p =  new Properties();
p.put("host", "localhost");
p.put("port", "7777");
ActorServer s = new ActorServer(p);
IPong pong = 
 s.newRemote("abs://pong@http://localhost:8888",
  IPong.class);
Ping ping = new Ping(pong);
ping.send(
  () -> ping.ping("")
);
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[caption=Remote pong actor main,label=lst:pong:remote]
Properties p = new Properties();
p.put("host", "localhost");
p.put("port", "8888");
ActorServer s = new ActorServer(p);
Pong pong = new Pong();
\end{lstlisting}
\end{minipage}
\end{center}

>>>>

\lstset{language=Java}
\begin{center}
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[caption=Ping as an interface,label=ch03:lst:ping:interface]
public interface IPing {
  void ping(String msg);
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[caption=Pong as an interface,label=ch03:lst:pong:interface]
public interface IPong {
  void pong(String msg);
}
\end{lstlisting}
\end{minipage}
\end{center}

@@

\lstset{language=Java}
\begin{center}
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[caption=Ping actor in Akka,label=ch03:lst:ping:akka]
public class Ping(ActorRef pong)
  extends UntypedActor 
  implements IPing {

@@

  public void onReceive(Object m) {
    if (!(m instanceof String)) {
      // Message not understood.
    } else 
    if (((String) m).startsWith("pinged") {
      // Explicit cast needed.
      ping((String) m);
    } 
   }
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[caption=Pong class in Akka,label=ch03:lst:pong:akka]
public class Pong 
  extends UntypedActor 
  implements IPong {

@@

\begin{figure}[h]
% \begin{wrapfigure}{r}{0.48\textwidth}
% \vspace{-20pt}
\begin{lstlisting}[caption=main in Akka,label=ch03:lst:main:akka]
ActorSystem s = ActorSystem.create();
ActorRef pong = s.actorOf(Props.create(Pong.class));
ActorRef ping = s.actorOf(Props.create(Ping.class, pong));
ping.tell(""); // To get a Future
\end{lstlisting}
% \vspace{-20pt}
% \end{wrapfigure}
\end{figure}

@@

\lstset{language=Java}
\begin{figure}[h]
% \begin{wrapfigure}{r}{0.48\textwidth}
% \vspace{-20pt}
\begin{lstlisting}[caption=main in ABS,label=ch03:lst:main:ABS]
ABSIPong pong;
pong = new ABSPong;
ping = new ABSPing(pong);
ping ! ping("");
\end{lstlisting}
% \vspace{-20pt}
% \end{wrapfigure}
\end{figure}

@@

\lstset{language=abs}
\begin{center}
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[caption=Ping in ABS,label=ch03:lst:ping:abs]
interface ABSIPing {
  Unit ping(String msg);
}
class ABSPing(ABSIPong pong) implements ABSIPing {
  Unit ping(String msg) {
  pong ! pong("ponged," + msg);
  }
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[caption=Pong in ABS,label=ch03:lst:pong:abs]
interface ABSIPong {
  Unit pong(String msg);
}
class ABSPong implements ABSIPong {
  Unit pong(String msg) {
    sender ! ping( "pinged," + msg);
  }
}
\end{lstlisting}
\end{minipage}
\end{center}
\lstset{language=Java}

@@

\begin{center}
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[caption=Actor interface (1) ,label=ch03:lst:j8:run]
public interface Actor {
  public void run() {
    Object m = queue.take();

@@

  // continue to the right
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[caption=Actor interface (2),label=ch03:lst:j8:enq]

@@

\paragraph{Modeling Asynchronous Messages} 
\label{ch03:par:asynchronous_messages}
We model an asynchronous call 
$$
\jtt{Future<V>} \; f = e_0\; !\; m(e_1,\ldots,e_n)
$$
to a method in ABS by the Java~8 code snippet of Listing \ref{ch03:lst:j8:call0}.
The final local variables $\jtt{u}_1$, $\ldots$, $\jtt{u}_n$ (of the caller) are used to store the values of
the Java~8 expressions $\jtt{e}_1$, $\ldots$, $\jtt{e}_n$ corresponding to the actual parameters  $e_1,\ldots,e_n$.
The types \jtt{T}$_i$, $i=1,\ldots,n$,  are the corresponding Java~8 types of  $e_i$, $i=1,\ldots,n$.
\begin{center}
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[mathescape,caption=Async messages with futures,label=ch03:lst:j8:call0]
final T$_1$ u$_1$ = e$_1$;
. . . 
final T$_n$ u$_n$ = e$_n$;
Future<V> v = e$_0$.send(
  () $\to$ { return m(u$_1$,$\ldots$,u$_n$); }
);
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[mathescape,caption=Async messages w/o futures,label=ch03:lst:j8:call1]
final T$_1$ u$_1$ = e$_1$;
. . . 
final T$_n$ u$_n$ = e$_n$;
e$_0$.send(
  { () $\to$ m(u$_1$,$\ldots$,u$_n$); }
);
\end{lstlisting}
\end{minipage}
\end{center}

@@

\begin{center}
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[mathescape, caption=Ping as an Actor,label=ch03:lst:ping]
public class Ping(IPong pong) implements IPing, Actor {
 public void ping(String msg) {
  pong.send( () $\to$ { pong.("ponged," + msg) } );
  }
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[mathescape, caption=Pong as an Actor,label=ch03:lst:pong]
public class Pong implements IPong, Actor {
  public void pong(String msg) {
    sender().send(( ) $\to$ { ping.("pinged," + msg) } );
  }
}
\end{lstlisting}
\end{minipage}
\end{center}

@@

\paragraph{Modeling Cooperative Scheduling}
The ABS statement $\bfjtt{await}\; g$, where $g$ is a boolean guard, allows an active object to preempt the current method and schedule another one.
% We describe the  translation of await statements in the context of a general translation of statements in the ABS language.
We model cooperative scheduling by means of a call to the \jtt{await} method in Listing~\ref{ch03:lst:j8:await}.
Note that the preempted process is thus passed as an additional parameter and as such queued in case the guard is false,
otherwise it is executed.
Moreover, the generation of the continuation of the process is an optimization task for the code generation process to prevent code duplication.
\begin{center}
\begin{minipage}[t]{0.48\textwidth}
% \begin{lstlisting}[mathescape, caption=Java~8 conceptual await,label=lst:j8:await]
%  this.await($b$, $()\rightarrow \{S\}$)
%  // S is the continuation
% \end{lstlisting}
\begin{lstlisting}[mathescape,caption=main in ABS API,label=ch03:lst:main:api]
IPong pong = new Pong();
IPing ping = new Ping(pong);
ping.send(
  () -> ping.ping("")
);
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[mathescape,caption=Java~8 await implementation,label=ch03:lst:j8:await]
void await(final Boolean guard, 
           final Runnable cont) {
  if (!guard) { 
    this.send(() $\to$ 
      { this.await(guard, cont) })
  } else { cont.run() }
}
\end{lstlisting}
\end{minipage}
\end{center}

@@

\begin{center}
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[caption=Remote ping actor main,label=ch03:lst:ping:remote]
Properties p =  new Properties();
p.put("host", "localhost");
p.put("port", "7777");
ActorServer s = new ActorServer(p);
IPong pong = 
 s.newRemote("abs://pong@http://localhost:8888",
  IPong.class);
Ping ping = new Ping(pong);
ping.send(
  () -> ping.ping("")
);
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\begin{lstlisting}[caption=Remote pong actor main,label=ch03:lst:pong:remote]
Properties p = new Properties();
p.put("host", "localhost");
p.put("port", "8888");
ActorServer s = new ActorServer(p);
Pong pong = new Pong();
\end{lstlisting}
\end{minipage}
\end{center}

### 2016-08-18 p03-ch01-2015-monitoring/sec045-defs.tex
Apply formatting and typography fixes
- Fix the mis-referenced listings and figures
- Fix typos

Signed-off-by: Behrooz Nobakht <nobeh5@gmail.com>

\lstset{language=java,aboveskip=-20pt,belowskip=-20pt}
\begin{figure}[h]
% \begin{wrapfigure}{r}{0.5\textwidth}
% \vspace{-15pt}
\begin{center}
\begin{lstlisting}[mathescape,caption=Platform API,label=lst:platform]
interface Platform {
  void    allocate(Service s);
  void    deallocate(Service s);
  Number  getState(Service s);
  boolean verify$_\alpha$(Service s);
  boolean verify$_\beta$(Service s);
}
\end{lstlisting}
\end{center}   
% \vspace{-15pt}
% \end{wrapfigure}
\end{figure}
\lstset{mathescape=false}
%

>>>>

\lstset{language=java}
\begin{figure}[h]
% \begin{wrapfigure}{r}{0.5\textwidth}
% \vspace{-15pt}
\begin{center}
\begin{lstlisting}[mathescape,caption=Platform API,label=ch04:lst:platform]
interface Platform {
  void    allocate(Service s);
  void    deallocate(Service s);
  Number  getState(Service s);
  boolean verify$_\alpha$(Service s);
  boolean verify$_\beta$(Service s);
}
\end{lstlisting}
\end{center}   
% \vspace{-15pt}
% \end{wrapfigure}
\end{figure}
\lstset{mathescape=false}
%

### 2016-08-18 p03-ch02-2014-jmseq/jmseq-elsa.tex
Apply formatting and typography fixes
- Fix the mis-referenced listings and figures
- Fix typos

Signed-off-by: Behrooz Nobakht <nobeh5@gmail.com>

\lstset{language=Java}
\begin{lstlisting}[label=lst:seq_obj, caption=SequencedObject Annotation Declaration]
@Retention(RetentionPolicy.RUNTIME)
@Target(ElementType.TYPE)
public @interface SequencedObject {
   // we need no properties for this annotation as this is only a marker.
}
\end{lstlisting}

@@

\lstset{language=Java}
\begin{lstlisting}[label=lst:seq_method, caption=SequencedMethod Annotation Declaration]
@Retention(RetentionPolicy.RUNTIME)
@Target(ElementType.METHOD)
public @interface SequencedMethod {

@@

\lstset{language=Java}
\begin{lstlisting}[label=lst:annotated_spec, caption=Sample annotated specification]

@@

\lstset{language=Java}
\begin{lstlisting}[label=lst:case-1-exceptions, caption=Exception
Specification for Case 1]
// Case 1
@SequencedObject
public class Main {

@@

\lstset{language=Java}
\begin{lstlisting}[label=lst:apples, caption=Apples JMSeq Specification]
@SequencedObject
public class Apples {

@@

\lstset{language=Java}
\begin{lstlisting}[label=lst:apples-junit, caption=Apples JMSeq JUnit
Test Unit]
public class ApplesDriver extends JUnit4Support {

@@

%Fredhopper Controller exposes an interface to prepare data, submit the data and then receive/collect the data job results.
\lstset{language=java}
\begin{lstlisting}[label=lst:frh:datadispatcher, caption=Controller Data Dispatcher Interface API]
interface DataDispatcher {
   Data create(Object object);
   Future<?> dispatch(String dataId);
   Future<?> dispatch(Data oid, String dataId);
}
\end{lstlisting}

The relevant part of the API of the Fredhopper Controller is presented in Listing \ref{ch05:lst:frh:datadispatcher}.
Customer applications use the interface to create a data object reference (using the \smalltt{create(Object)} method) and then use the created data reference to start a data job (using the overloaded \smalltt{dispatch} method, which has an optional \smalltt{Data} parameter).
Note that the dispatch method allows for two different uses by the customer, for instance in Listing~\ref{ch05:lst:frh:c1} the data job to be executed performs only a rebuild of the customer's product catalog and as such does not need to have a data reference.
\lstset{language=java}
\begin{lstlisting}[label=lst:frh:c1, caption=A use case with no data requirement]
class CustomerApp {
   public void rebuildCatalog() {
      Future<?> result = 
         dispatcher.dispatch("reindex");
      // further processing of result
   }
}
\end{lstlisting}
If the customer needs to update their catalog with new products, then first a data reference is created. This reference is used to initiate a data job, as described in Listing \ref{ch05:lst:frh:c2}.
\lstset{language=java}
\begin{lstlisting}[label=lst:frh:c2, caption=A use case with data requirement]
class CustomerApp {
   public void updateCatalog(Catalog catalog) {
      Data data = dispatcher.create(catalog);
      Future<?> result = 
         dispatcher.dispatch(data.getId(), "update");
      // further processing of result
   }
}
\end{lstlisting}

@@

\lstset{language=java}
\begin{lstlisting}[float=t,label=lst:frh:c3, caption=How to verify Fredhopper API usage]
@SequencedObject
class CustomerAppDriver {

@@

\lstset{language=[AspectJ]Java, morekeywords={suffix, event,ere, CFG, @fail, @match, __RESET}} 
\begin{lstlisting}[label=lst:frh:jmop, caption=Fredhopper case study with JavaMOP]
UpdateCatalog(Catalog catalog) {
   event create_data before(DataDispatcher d):
      call(* DataDispatcher.create(..)) && target(d) {}

@@

We use JMSeq to verify an example code for this scenario. 
We use the code snippet displayed in Listing \ref{ch05:lst:jmseq-iter} that uses JMSeq annotations to express the correct usage. 
In the code, we use a variable \smalltt{count} to control the number of times \smalltt{hasNext()} is called before there is a call to \smalltt{next()}. 
This example always passes the JMSeq verification with success. 
For performance measurements, we study the ``correct'' use of the example while verification of wrong usages are also possible. 
\lstset{language=Java}
\begin{lstlisting}[label=lst:jmseq-iter, caption=Iterator usage with
JMSeq Annotations]
   @SequencedMethod(
     value = "{call(* java..Vector.iterator())}$"
         + "{call(* java..Iterator.hasNext())}$"
         + "{call(* java..Iterator.next())}", 
        allowExceptions = false)
   public void visitAllElements() {
      Iterator<Integer> i = v.iterator();
      for (int k = 0; k < count && i.hasNext(); ++k) {
         i.hasNext();
         i.next();
      }
   }
\end{lstlisting}

@@

% \lstset{language=[AspectJ]Java, morekeywords={suffix, event,ere, CFG, @fail, @match, __RESET}} \begin{lstlisting}[label=lst:sample_mop, caption=Sample JavaMOP Specification using CFG logic] // Case 1
% SampleCase1(Main m) {
%  event method_m_a before(A a):
%     call(* A.m_a(..)) && target(a) {}

>>>>

\lstset{language=Java}
\begin{lstlisting}[label=ch05:lst:seq_obj, caption=SequencedObject Annotation Declaration]
@Retention(RetentionPolicy.RUNTIME)
@Target(ElementType.TYPE)
public @interface SequencedObject {
   // we need no properties for this annotation as this is only a marker.
}
\end{lstlisting}

@@

\lstset{language=Java}
\begin{lstlisting}[label=ch05:lst:seq_method, caption=SequencedMethod Annotation Declaration]
@Retention(RetentionPolicy.RUNTIME)
@Target(ElementType.METHOD)
public @interface SequencedMethod {

@@

\lstset{language=Java}
\begin{lstlisting}[label=ch05:lst:annotated_spec, caption=Sample annotated specification]

@@

\lstset{language=Java}
\begin{lstlisting}[label=ch05:lst:case-1-exceptions, caption=Exception
Specification for Case 1]
// Case 1
@SequencedObject
public class Main {

@@

\lstset{language=Java}
\begin{lstlisting}[label=ch05:lst:apples, caption=Apples JMSeq Specification]
@SequencedObject
public class Apples {

@@

\lstset{language=Java}
\begin{lstlisting}[label=ch05:lst:apples-junit, caption=Apples JMSeq JUnit
Test Unit]
public class ApplesDriver extends JUnit4Support {

@@

%Fredhopper Controller exposes an interface to prepare data, submit the data and then receive/collect the data job results.
\lstset{language=java}
\begin{lstlisting}[label=ch05:lst:frh:datadispatcher, caption=Controller Data Dispatcher Interface API]
interface DataDispatcher {
   Data create(Object object);
   Future<?> dispatch(String dataId);
   Future<?> dispatch(Data oid, String dataId);
}
\end{lstlisting}

The relevant part of the API of the Fredhopper Controller is presented in Listing \ref{ch05:lst:frh:datadispatcher}.
Customer applications use the interface to create a data object reference (using the \smalltt{create(Object)} method) and then use the created data reference to start a data job (using the overloaded \smalltt{dispatch} method, which has an optional \smalltt{Data} parameter).
Note that the dispatch method allows for two different uses by the customer, for instance in Listing~\ref{ch05:lst:frh:c1} the data job to be executed performs only a rebuild of the customer's product catalog and as such does not need to have a data reference.
\lstset{language=java}
\begin{lstlisting}[label=ch05:lst:frh:c1, caption=A use case with no data requirement]
class CustomerApp {
   public void rebuildCatalog() {
      Future<?> result = 
         dispatcher.dispatch("reindex");
      // further processing of result
   }
}
\end{lstlisting}
If the customer needs to update their catalog with new products, then first a data reference is created. This reference is used to initiate a data job, as described in Listing \ref{ch05:lst:frh:c2}.
\lstset{language=java}
\begin{lstlisting}[label=ch05:lst:frh:c2, caption=A use case with data requirement]
class CustomerApp {
   public void updateCatalog(Catalog catalog) {
      Data data = dispatcher.create(catalog);
      Future<?> result = 
         dispatcher.dispatch(data.getId(), "update");
      // further processing of result
   }
}
\end{lstlisting}

@@

\lstset{language=java}
\begin{lstlisting}[float=t,label=ch05:lst:frh:c3, caption=How to verify Fredhopper API usage]
@SequencedObject
class CustomerAppDriver {

@@

\lstset{language=[AspectJ]Java, morekeywords={suffix, event,ere, CFG, @fail, @match, __RESET}} 
\begin{lstlisting}[label=ch05:lst:frh:jmop, caption=Fredhopper case study with JavaMOP]
UpdateCatalog(Catalog catalog) {
   event create_data before(DataDispatcher d):
      call(* DataDispatcher.create(..)) && target(d) {}

@@

We use JMSeq to verify an example code for this scenario. 
We use the code snippet displayed in Listing \ref{ch05:lst:jmseq-iter} that uses JMSeq annotations to express the correct usage. 
In the code, we use a variable \smalltt{count} to control the number of times \smalltt{hasNext()} is called before there is a call to \smalltt{next()}. 
This example always passes the JMSeq verification with success. 
For performance measurements, we study the ``correct'' use of the example while verification of wrong usages are also possible. 
\lstset{language=Java}
\begin{lstlisting}[label=ch05:lst:jmseq-iter, caption=Iterator usage with
JMSeq Annotations]
   @SequencedMethod(
     value = "{call(* java..Vector.iterator())}$"
         + "{call(* java..Iterator.hasNext())}$"
         + "{call(* java..Iterator.next())}", 
        allowExceptions = false)
   public void visitAllElements() {
      Iterator<Integer> i = v.iterator();
      for (int k = 0; k < count && i.hasNext(); ++k) {
         i.hasNext();
         i.next();
      }
   }
\end{lstlisting}

@@

% \lstset{language=[AspectJ]Java, morekeywords={suffix, event,ere, CFG, @fail, @match, __RESET}} \begin{lstlisting}[label=ch05:lst:sample_mop, caption=Sample JavaMOP Specification using CFG logic] // Case 1
% SampleCase1(Main m) {
%  event method_m_a before(A a):
%     call(* A.m_a(..)) && target(a) {}
